### 2023-06-10 README.Rmd
230610_v01

👉🏾 <u>What you need to provide</u>: <br> After collecting your data, and
running your initial *Hierarchical Bayes* models, you can turn to
<code>validateHOT</code> and test how good your model predicts choices
in the validation/ holdout task. Herefore, you only have to insert your
**raw** utility scores as well as the actual choice of your validation/
holdout task. You can use the <code>merge()</code> provided by
<code>base</code> package [@base]. Afterward, you can read in your data
file and enjoy <code>validateHOT</code>.

👈🏾 <u>What you get</u>:<br> At the moment, <code>validateHOT</code>
provides functions for 3 key areas:

@@

<li><code>kl</code>: Kullback-Leibler-Divergence ?????? [@ding2011]. If
you specify an optional <code>Group</code> argument the output is split
by groups.</li>

@@

<li><code>mhp</code>:</li>

<li><code>rmse</code>:</li>

@@

<li><code>freqassort</code>:</li>

<li><code>reach</code>:</li>

<li><code>shareofpref</code>:</li>

@@

<li><code>ACBC_interpolate</code>:</li>

<li><code>ACBC</code>:</li>

<li><code>CBC_lin</code>:</li>

<li><code>CBC</code>:</li>

<li><code>MaxDiff</code>:</li>

@@

<li><code>createHOT</code>: creates the validation/holdout task for you.
For example, in a *CBC* the total utilities are calculated by the sum of
each attribute level. You have to specify the attribute levels for each
alternative in the validation/holdout task and it will calculate the
total utility for each alternative in the validation/holdout task.</li>

>>>>

👉🏾 <u>**What you need to provide**</u>: <br> After collecting your data,
and running your initial *Hierarchical Bayes* models, you can turn to
<code>validateHOT</code> and test how good your model predicts choices
in the validation/ holdout task. Herefore, you only have to insert your
**raw** utility scores as well as the actual choice of your validation/
holdout task. You can use the <code>merge()</code> provided by
<code>base</code> package [@base]. Afterward, you can read in your data
file and enjoy <code>validateHOT</code>.

👈🏾 <u>**What you get**</u>:<br> At the moment, <code>validateHOT</code>
provides functions for 3 key areas:

@@

<li><code>kl</code>: Kullback-Leibler-Divergence which measures the
divergence between the actual choice distribution and the predicted
choice distribution [@ding2011; @philentropy]. Output provides both
divergence between *predicted* from *observed* and *observed* from
*predicted* due to the asymmetry of the Kullback-Leibler divergence. If
you specify an optional <code>Group</code> argument the output is split
by groups.</li>

@@

<li><code>rmse</code>: provides the root-mean-squared error of deviation between predicted and stated choice share. If you specify an optional <code>Group</code> argument the output is split by groups.</li>

@@

<li><code>freqassort</code>: Inspired by the former [*turfR*](https://github.com/cran/turfR) package, <code>freqassort</code> will give you the averaged frequency, how many products the participants will choose from your in the function determined potential assortment. For the <code>method</code> argument you can decide between <code>method = "threshold"</code> (if utility of product is larger than the utility of *none*, it is marked as potential purchase option) and <code>method = "First Choice"</code> (only product with highest utility is considered. If its utility is above the utility of *none*, it is marked as potential purchase option). If you specify an optional <code>Group</code> argument the output is split by groups.</li>

<li><code>reach</code>: Inspired by the former [*turfR*](https://github.com/cran/turfR) package, <code>reach</code> will give you the averaged percentage of how many participants you can reach (buy *at least* one of the products) with your in the function determined potential assortment. or the <code>method</code> argument you can decide between <code>method = "threshold"</code> (if utility of product is larger than the utility of *none*, it is marked as potential purchase option) and <code>method = "First Choice"</code> (only product with highest utility is considered. If its utility is above the utility of *none*, it is marked as potential purchase option). If you specify an optional <code>Group</code> argument the output is split by groups.</li>

<li><code>shareofpref</code>: provides you the aggregated share of preference, including the lower and upper confidence interval, which is calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$. If you specify an optional <code>Group</code> argument the output is split by groups and provided in a <code>list</code> element. </li>

@@

<li><code>ACBC</code>: Example data set with raw utilities of an *ACBC* study conducted in Sawtooth. Price was linear-coded while the other attributes were coded as part-worths.</li>

<li><code>ACBC_interpolate</code>: Example data set with raw utilities of an *ACBC* study conducted in Sawtooth. Price was piecewise-coded, another attribute was linear-coded while the other attributes were coded as part-worths. </li>

<li><code>CBC</code>: Example data set with raw utilities of an *CBC* study conducted in Sawtooth. All attributes were coded as part-worth.</li>

<li><code>CBC_lin</code>: Example data set with raw utilities of an *CBC* study conducted in Sawtooth. One attribute was linear coded while the other attributes are part-worth coded.</li>

<li><code>MaxDiff</code>: Example data set with raw utilities of an *MaxDiff* study conducted in Sawtooth.</li>

@@
